---
title: "My_NOAA_vignette"
author: "Anoushiravan Razmavar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{My_NOAA_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `noaar` package has been built for cleaning and mapping NOAA's Significant Earthquake data. 

## Installation

In order to install the `noaar` package, the user must first install the
`devtools` package and then use the following commands:

```{r eval=FALSE}
devtools::install_github("AnoushiravanR/noaar")
library(noaar)
```

## Required packages

For codes in `noaar` package to work the following packages are required:

```{r setup, warning=FALSE, message=FALSE}
library(noaar)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(lubridate)
library(purrr)
library(rlang)
library(grid)
library(leaflet)
library(tibble)
```

## Load and clean package data

For loading the `NOAA_data` you can use `noaar::NOAA_data`, then you can 
call `eq_clean_data` and `eq_location_clean` to do some modifications on a 
number of variables. After that the data can be used for geom functions.

```{r}
NOAA_data <- noaar::NOAA_data
NOAA_data <- NOAA_data %>%
  eq_clean_data() %>%
  eq_location_clean()
NOAA_data %>%
  dplyr::select(1:10)
```



A brief description of the variables that are used for data analysis are presented
in the table bellow:



```{r results='asis', echo=FALSE}

knitr::kable(tibble::tribble(~ Variable, ~ Class, ~ Description,
                             "Date", "Date", "The date in which the earthquake occurred",
                             "Country", "Character", "The Country in which the earthquake occurred",
                             "Location", "Character", "The place(normally city) in which the earthquake occurred",
                             "Longitude", "Numeric", "The longitude of the location",
                             "Latitude", "Numeric", "The latitude of the location", 
                             "Mag", "Numeric", "The magnitude of earthquake based on the Richter scale",
                             "Deaths", "Numeric", "The number of casualties(deaths)"), 
             caption = "The Principal Variables Required for Visualization")


```


## Geoms

### geom_timeline

You can  use the following code to make a time line geom of a single or multiple 
countries within a specific time intervals:

```{r fig.width=7, fig.align='center'}
NOAA_data %>%
  dplyr::filter(Country %in% c("MEXICO", "IRAN") &
           Date %within% lubridate::interval(ymd(20000103), ymd(20180104))) %>%
  dplyr::mutate(Country = factor(Country, levels = unique(Country))) %>%
  ggplot2::ggplot() +
  geom_timeline(aes(x = Date, y = Country, size = Mag, colour = Deaths)) +
  ggplot2::scale_colour_continuous(name = "# deaths") +
  ggplot2::scale_size_continuous(name = "Richter scale value") +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::ylab("")

```

### geom_timeline_label

This geom function also enables you to map a time line of a single or multiple 
countries within a specific time interval, additionally, it has a new aesthetic 
`n_max` which you can adjust for labeling the n biggest earthquakes.


```{r fig.width=7, fig.align='center'}
NOAA_data %>%
  dplyr::filter(Country %in% c("MEXICO", "IRAN") &
           Date %within% lubridate::interval(ymd(20000103), ymd(20180104))) %>%
  dplyr::mutate(Country = factor(Country, levels = unique(Country))) %>%
  ggplot2::ggplot() +
  geom_timeline(aes(x = Date, y = Country, size = Mag, colour = Deaths)) +
  geom_timeline_label(aes(x = Date, y = Country, label = Location,
                          magnitude = Mag, colour = Deaths, n_max = 5), alpha = 0.5) +
  ggplot2::scale_colour_continuous(name = "# deaths") +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::ylab("")

```

Note that you can combine these two geoms or use them seperately.

## Plot Map

### Using a column for annotation

You can create an interactive leaflet map with `eq_map` function. You can also
annotate the locations by using `annot_col` argument and adjusting a column to 
it. It should be noted that `annot_col` requires a character vector. 

```{r fig.width=7, fig.align='center'}
NOAA_data %>%
  dplyr::filter(Country == "MEXICO" & lubridate::year(Date) >= 2000) %>%
  eq_map(annot_col = "Date")

```

### Using a more interesting and informative annotation 

For more customized and informative labels you can create a new variable in 
the data set using some HTML-formatting to create character string for the 
`annot_col` parameter. 

```{r fig.width=7, fig.align='center'}
NOAA_data %>%
  dplyr::filter(Country %in% c("HONDURAS", "MEXICO") & year(Date) >= 2000) %>%
  dplyr::mutate(popup_text = eq_create_label(.)) %>%
  eq_map(annot_col = "popup_text")

```





